Generalized Universe Hierarchies and First-Class Universe Levels

### 2021-03-18 paper.tex
last edit
typo

We may think about the relation between \emph{modalities} and morphisms. The
main difference is that we have no structural restrictions on variables and
contexts. More concretely, every $\Lift$ is dependent right adjoint
\cite{dependentrightadjoints} to the identity functor on the base category, as
we have $\Tm\,(\msf{Id}\,\Gamma)\,A \simeq \Tm\,\Gamma\,(\Lift\,A)$. Hence,
every morphism can be viewed as a degenerate modality.

@@

Second, we only focus on using universes as sized-based classifiers for
types. Stratification features are also present in two-level type theory
\cite{twolevel}, modal type theories \cite{gratzer20multimodal} or as h-levels
in homotopy type theory \cite{hottbook}. It would be interesting to port
universe features in this paper to two-level type theory, as they would
hopefully model a form of stage polymorphism in multi-stage compilation. We
could try representing $\msf{Prop}$ universes in TTFL as well. This is closely
related to h-level based stratification.

>>>>

We may think about the relation between \emph{modalities} and morphisms. The
main difference is that morphisms impose no structural restrictions on variables
and contexts. More concretely, every $\Lift$ is dependent right adjoint
\cite{dependentrightadjoints} to the identity functor on the base category, as
we have $\Tm\,(\msf{Id}\,\Gamma)\,A \simeq \Tm\,\Gamma\,(\Lift\,A)$. Hence,
every morphism can be viewed as a degenerate modality.

@@

Second, we only focus on using universes as size-based classifiers for
types. Stratification features are also present in two-level type theory
\cite{twolevel}, modal type theories \cite{gratzer20multimodal} or as h-levels
in homotopy type theory \cite{hottbook}. It would be interesting to port
universe features in this paper to two-level type theory, as they would
hopefully model a form of stage polymorphism in multi-stage compilation. We
could try representing $\msf{Prop}$ universes in TTFL as well. This is closely
related to h-level based stratification.
